Fair Decision Making

### 2023-06-17 Notes/paper_notes.tex
Updated day 12.

>>>>

\subsection{\href{https://arxiv.org/pdf/2110.02711.pdf}{DiffusionCLIP: Text-Guided Diffusion Models for Robust Image Manipulation}}

\begin{approach*}
\textbf{DiffusionCLIP} performs text-driven image manipulation using diffusion models. Based on
full inversion capability and high-quality image generation power of recent diffusion models, the method performs zeroshot image manipulation successfully even between unseen domains. The authors propose a novel noise combination
method that allows straightforward multi-attribute manipulation. Code is available in their
\href{https://github.com/gwang-kim/DiffusionCLIP.git}{DiffusionCLIP GitHub}
\end{approach*}

Other ``state-of-the-art text-driven manipulation methods" include TediGAN, StyleCLIP, and \href{https://arxiv.org/pdf/2108.00946.pdf}{StyleGAN-NADA} (which leverages GAN inversion and CLIP loss to achieve image manipulation that does not require additional training with simple text prompts).

\section{Summary of Work So Far}

\subsection{Face Detectors}

Existing Facial Detection Algorithms are evaluated on the widely known \href{http://shuoyang1213.me/WIDERFACE/index.html}
{WIDER FACE} (Face Detection Benchmark Dataset). A number of Facial Detection Algorithms and their evaluations on WIDER FACE can be found \href{http://shuoyang1213.me/WIDERFACE/WiderFace_Results.html}{here}. Note that some of these algorithms are object detection algorithms adapted for facial recognition, but some are also specifically facial detectors (e.g. RetinaFace, YOLO5Face).
